---
title: "EDA Assignment Prep"
author: "Amber Camp"
format: html
editor: visual
---

## EDA Assignment Prep: Pokemon data

### Libraries

```{r}
library(here)
library(tidyverse)
library(janitor)
```

### Data

```{r}
pokedata <- read_csv(here("data/Pokemon.csv"))

pokedata <- pokedata %>%
  clean_names()
```

### Describe the data:

Data author:

Description:

How many observations (rows) are there?

How many variables (columns) are there?

### skimr: Quick overview

```{r}
skim_data <- skimr::skim(pokedata)
```

### Summary: Quick overview

```{r}
summary(pokedata)
```

### Categorical vs. Continuous

```{r}
class(pokedata$number) #checks class
pokedata$number <- as.factor(pokedata$number) #converts to factor
class(pokedata$number)
summary(pokedata$number)

summary(pokedata$type_1)
pokedata$type_1 <- as.factor(pokedata$type_1)
class(pokedata$type_1)
summary(pokedata$type_1)

summary(pokedata$generation)

```

How many categorical variables are there? 5 maybe 6

How many continuous variables are there? 7

What are some variables of interest to you?

------------------------------------------------------------------------

## EDA Assignment Prep: \[Insert Data Name Here\]

### Libraries

```{r}
library(here)
library(tidyverse)
library(janitor)
```

### Data

```{r}

```

### Describe the data:

Data author:

Description:

How many observations (rows) are there?

How many variables (columns) are there?

### Summary: Quick overview

```{r}

```

### Categorical vs. Continuous

```{r}

```

How many categorical variables are there?

How many continuous variables are there?

What are some variables of interest to you?
