---
title: "Homework 8: Class Wrap-up"
format: html
editor: visual
---

## Homework 8: Class Wrap-up

We are finally at the end of the semester! The final homework for the class will be to summarize and share some of the things we've done so far.

The plan is for everyone to be randomly paired with a tiny topic pertaining to something we've learned together this semester and then submit a code snippet to be presented in class on Wednesday, 11/20.

#### Libraries

```{r, message=FALSE}
library(tidyverse)
library(here)
```

#### Read in the list of topics

```{r, message=FALSE}
topics <- read_csv("cs201_topics.csv")
view(topics)

# anything to edit?
#topics[#, "topic"] <- 
```

#### Read in the list of student names

```{r, message=FALSE}
names <- read_csv("cs201_names.csv")
view(names)
```

#### Generate a random number in the names dataframe

```{r, message=FALSE}
names <- names %>%
  mutate(number = sample(1:8, nrow(names), replace = FALSE))

view(names)
```

#### Join the names to the topics

```{r, message=FALSE}
assigned_topics <- names %>%
  full_join(topics, by = "number")

view(assigned_topics)
```

### Instructions

1.  Find your assigned topic. Talk to me if you reeeeeeaaaally want to do something else, or trade with someone (but let me know).

2.  Prepare a code snippet that briefly (2-3 mins) explains the topic in the code chunk below, using `penguins` data.

3.  Push to GitHub BY NOON on Wednesday 11/20 (I'll need time to download and compile before class).

4.  Come to class next Wednesday and show us how it's done :)

#### Extra libraries needed (if any)

```{r, message=FALSE}
library(janitor)

```

#### Read in penguins data

```{r, message=FALSE}
penguins <- read_csv(here("data/penguins_lter.csv"))

penguins <- penguins %>% 
  clean_names()
```

#### {Insert topic here}

```{r, message=FALSE}
# insert code snippet here

```
